\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-2pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-2pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%==== Profile ====%
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
	\textbf{{\LARGE Gavin Mak}} & gavinmak98@gmail.com\\
	Software Engineer & gavinmak.com\\
	& (781) 389-2000\\
\end{tabular*}
\vspace{4mm}


%==== Experience ====%
\header{{\large Experience}}
\vspace{2mm}

\textbf{Google} \hfill San Francisco, CA\\
\vspace{1mm}
\textit{Software Engineer} \hfill \textit{Aug 2020 - Present}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Led a multi-quarter initiative to integrate a modernized UX for continuous integration testing, improving developer workflow and efficiency.
	\item Maintained open-source developer tools for Chrome development and contributed to the strategic planning for their ongoing development.
	\item Joined two on-call rotations overseeing Chrome’s infrastructure and repositories. Responsible for build monitoring, issue triaging, and managing escalations.
\end{itemize}

\textbf{Google} \hfill Bellevue, WA\\
\vspace{1mm}
\textit{Software Engineer Intern} \hfill \textit{Aug 2019 - Nov 2019}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Spearheaded an experiment to integrate open-source Chrome tests into Google\textquotesingle{}s internal infrastructure, enhancing test coverage and accelerating bug detection.
\end{itemize}

\textbf{Wayfair} \hfill Boston, MA\\
\vspace{1mm}
\textit{Software Engineer Intern} \hfill \textit{June 2019 - Aug 2019}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Built a comprehensive tool to streamline Apache Kafka topic management using React, Java Spring, and MariaDB, superseding the former CLI.
	\item Achieved a 97\% reduction in topic creation time, saving over 8 hours on average.
\end{itemize}

\textbf{SAP} \hfill San Ramon, CA\\
\vspace{1mm}
\textit{Software Developer Intern} \hfill \textit{June 2018 - Aug 2018}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Enabled connections between SAP HANA and PostgreSQL databases, facilitating real-time data transfer, and benefiting clients such as Coca Cola, Decathlon, and Miele.
	\item Ensured seamless integration by creating custom query translations and data type mappings to bridge functionality gaps.
\end{itemize}
\vspace{4mm}


%==== Education ====%
\header{{\large Education}}
\vspace{2mm}
\textbf{University of California, Berkeley}\hfill Berkeley, CA\\
\vspace{1mm}
\textit{Bachelor of Arts, Computer Science} | \textit{GPA: 3.8} \hfill \textit{May 2020}\\
\vspace{2mm}
\textbf{Honors}: Upsilon Pi Epsilon Honor Society (Top 1/3 of CS majors)\\
\vspace{6mm}


%==== Projects ====%
\header{{\large Projects}}
\vspace{2mm}

{\textbf{Poster}} \hfill {\sl Flutter, MongoDB, Firebase Auth} \\
\vspace{1mm}
Built a social media app for medium to long format text posts on iOS and Android. Designed a content recommendation algorithm based on user preferences. \\
\vspace*{2mm}

{\textbf{gavinmak.com}} \hfill {\sl HTML5, CSS, JavaScript} \\
\vspace{1mm}
Created a personal website with responsive web design in mind. Automatically uses dark mode based on browser settings.\\
\vspace*{2mm}

{\textbf{Curreta}} \hfill {\sl Django, React Native} \\
\vspace{1mm}
Developed a web and mobile app for a crowdsourced, real-time public transit tracker. Used the GeoDjango API along with BART and AC Transit schedules to provide live locations for the Bay Area.\\
\vspace*{2mm}

\vspace*{4mm}


%==== Skills ====%
\header{{\large Skills}}
\vspace{2mm}

\begin{tabular}{@{}lll@{}}
	{\textbf{Languages}}:  Python, JavaScript, Go, Java, Dart, SQL & {\textbf{Tools}}: Git, Flutter, React, MongoDB, Figma \\
\end{tabular}

\end{document}
